\documentclass[a4paper,online,extended]{adcv}
% \documentclass[a4paper,online]{adcv}

\usepackage[british]{babel}

\usepackage{needspace}

% Disable hyphenation globally
\usepackage[none]{hyphenat}
\hyphenpenalty=10000
\exhyphenpenalty=10000

\newcommand{\todayMonthYear}{\ifcase \month \or January\or February\or March\or April\or May%
\or June\or July\or August\or September\or October\or November\or December\fi\ %
\number \year}

\newcommand*{\unistb}{Stellenbosch University}

\title{Marcel Roux -- Resume}

\adcvname{Marcel}{Roux}
\adcvtitle{Senior Software Engineer — High-Throughput Distributed Systems}
\adcvaddress{}{Alberta}{Canada}{}
\adcvemail{marcel.roux.email}{gmail}{com}
\adcvlinkedin{https://www.linkedin.com/in/}{rouxmarcel}
\adcvgithub{https://github.com/}{MarcelRoux}
\adcvphone{(+1) 403 373 5492}
\adcvdate{\todayMonthYear}

\begin{document}
\selectlanguage{british}

% ======================================================
% SUMMARY
% ======================================================
{\raggedright
Senior software engineer with 8+ years of professional experience building and operating data-intensive, correctness-sensitive distributed systems with high concurrency and strict ordering guarantees. Specialised in event-driven ingestion pipelines, stream processing, and backend APIs where performance, fault tolerance, and operational reliability are critical.

Recent work focused on large-scale blockchain data ingestion and analytics platforms, delivering end-to-end production ownership using Rust, Python, Kafka, ClickHouse, and Postgres.
\par}
% ======================================================
% EXPERIENCE
% ======================================================

\section{Experience}

\begin{adcvtabletwo}

% ---------------- Vybe Network ----------------

\adcvrowtwo{\textbf{Data Engineering Team Lead}, Vybe Network — Vancouver, BC, Canada}{2025--2026}
\ifextended
  \adcvrowmulti{• Led a team of \textbf{3 engineers (4 including myself)} responsible for blockchain ingestion systems, analytics pipelines, and data APIs.}
  \adcvrowmulti{• Planned epics and technical priorities aligned with business OKRs, balancing feature delivery, reliability, and technical debt.}
  \adcvrowmulti{• Owned on-call operations and incident response for customer-facing systems, driving post-incident reviews and reliability improvements.}
  \adcvrowmulti{• Coordinated cross-team initiatives across data science, product, and platform engineering.}
  \adcvrowmulti{• Remained hands-on with system design while mentoring engineers and improving CI/CD and documentation standards.}
\else
  \adcvrowmulti{• Led a team of 3 engineers (4 including myself) owning blockchain ingestion, analytics pipelines, and customer-facing data APIs.}
  \adcvrowmulti{• Planned delivery against OKRs while maintaining on-call ownership, incident response and post-incident reliability improvements.}
\fi
\adcvrowskip

\adcvrowtwo{\textbf{Senior Software Engineer}, Vybe Network — Vancouver, BC, Canada}{2023--2025}
\ifextended
  \adcvrowmulti{• Designed and operated event-driven, streaming ingestion pipelines processing \textbf{thousands of transactions per second} with strict ordering and correctness guarantees.}
  \adcvrowmulti{• Built Python-based live transaction and account parsers backed by Kafka, Postgres, and Kubernetes in production.}
  \adcvrowmulti{• Contributed to a Rust- and ClickHouse-based ingestion architecture, implementing concurrent, fault-tolerant pipelines with explicit backpressure and correctness-preserving offset management.}
  \adcvrowmulti{• Developed extensible protocol parsing frameworks, scaling supported protocols from single digits to \textbf{50+ protocols}.}
  \adcvrowmulti{• Built production internal and public backend APIs using FastAPI and Actix Web, including caching, access control, and rate limiting.}
  \adcvrowmulti{• Improved observability and operational insight through Prometheus and Grafana adoption.}
\else
  \adcvrowmulti{• Designed and operated Solana ingestion pipelines processing thousands of transactions per second with strict ordering and correctness guarantees.}
  \adcvrowmulti{• Built concurrent, fault-tolerant Rust + ClickHouse ingestion paths with explicit backpressure and offset management.}
  \adcvrowmulti{• Delivered production backend APIs and stream processors using Kafka, Postgres, FastAPI, and Actix Web.}
\fi
\adcvrowskip

% ---------------- ExploreAI ----------------

\adcvrowtwo{\textbf{Senior Data Engineer}, ExploreAI — Cape Town, South Africa}{2021--2023}
\ifextended
  \adcvrowmulti{• Built highly parallelised model training and inference workflows using Spark, MLflow, and scikit-learn, reducing runtimes from days to minutes.}
  \adcvrowmulti{• Developed robust ETL pipelines with Azure Data Factory and PySpark for large-scale time-series datasets.}
  \adcvrowmulti{• Introduced data lineage, metadata capture, and governance patterns used across multiple production projects.}
\fi
\adcvrowskip

\adcvrowtwo{\textbf{Data Engineer}, ExploreAI — Cape Town, South Africa}{2020--2021}
\ifextended
  \adcvrowmulti{• Performed extensive exploratory data analysis to inform downstream analytics and modelling.}
  \adcvrowmulti{• Developed time-series anomaly detection models identifying operational issues ahead of production baselines.}
  \adcvrowmulti{• Improved performance of strategic optimisation models, reducing execution time from weeks to hours.}
\fi
\adcvrowskip

% ---------------- BridgIoT ----------------

\adcvrowtwo{\textbf{Software Engineer}, BridgIoT — Stellenbosch, South Africa}{2017--2020}
\ifextended
  \adcvrowmulti{• Re-architected reporting systems to serverless AWS Lambda, reducing compute costs by \textbf{~80\%}.}
  \adcvrowmulti{• Designed and built containerised APIs and reporting engines using Python, Flask, Docker, ECS, and S3.}
  \adcvrowmulti{• Implemented ingestion layers for heterogeneous IoT protocols (LoRa, SIGFOX, GSM, NB-IoT) using MQTT-based architectures.}
  \adcvrowmulti{• Established CI/CD pipelines and optimised container builds, reducing deployment times by \textbf{~90\%}.}
\fi

\end{adcvtabletwo}

% ======================================================
% EDUCATION
% ======================================================

\section{Education}

\begin{adcvtabletwo}
  \adcvrowtwo{\textbf{Master of Engineering (MEng), Electrical and Electronic Engineering (\textit{cum laude})}, \unistb}{2017}
  \ifextended
    \adcvrowmulti{Dissertation: Optimisation of Electric Water Heater Demand-Side Management through Smart Grid and Predictive Scheduling.}
  \fi
  \adcvrowskip

  \adcvrowtwo{\textbf{Bachelor of Engineering (BEng), Electrical and Electronic Engineering}, \unistb}{2015}
\end{adcvtabletwo}

% ======================================================
% TECHNICAL SKILLS
% ======================================================

\needspace{5\baselineskip}
\section{Technical Skills}

\begin{adcvtablethree}
  \adcvrowthree{\textbf{Languages:}}{Rust, Python, SQL}{}
  \adcvrowskip

  \adcvrowthree{\textbf{Distributed Data Systems:}}{Kafka, ClickHouse, Postgres, Redis}{}
  \adcvrowskip

  \adcvrowthree{\textbf{Workflow \& Data Pipelines:}}{Airflow}{}
  \adcvrowskip

  \adcvrowthree{\textbf{Backend \& APIs:}}{Actix Web, FastAPI, Flask}{}
  \adcvrowskip

  \adcvrowthree{\textbf{Infrastructure \& Operations:}}{Docker, Kubernetes, CI/CD, AWS, GCP, Azure}{}
\end{adcvtablethree}

% ======================================================
% LANGUAGES
% ======================================================

\section{Languages}

English (Fluent) \quad Afrikaans (Fluent)

\end{document}